Abstract Binding Trees

### 2015-10-22 paper.tex
clarification

Then, fix a covariant presheaf of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Psi : C\to\Sets$ but we keep the $C$
  implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
  $C\Grothendieck{}{\Psi} \cong \int^{c \in C}c / C \otimes
  \Discrete{\Psi(c)}$.} $\Grothendieck{}{(-)} : \Sets^{C}\to\Cats$ on operators
we have a category of objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck fibration and $ap_{\Singleton}$ is the forgetful functor from pointed sets:

@@

Operators are defined by specifying the fibres of $\Grothendieck{}{\Operators}$ in which
they reside. For instance, consider the lambda calculus with a single sort,
$\SortExp$; we give its signature by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\lambda}{
    \MkArity{\MkValence{\cdot}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathsf{ap}}{
    \MkArity{
      \MkValence{\cdot}{\cdot}{\SortExp},
      \MkValence{\cdot}{\cdot}{\SortExp}
    }{\SortExp}
  }
\end{gather*}

>>>>

Then, fix a covariant presheaf (copresheaf) of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Psi : C\to\Sets$ but we keep the $C$
  implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
  $C\Grothendieck{}{\Psi} \cong \int^{c \in C}c / C \otimes
  \Discrete{\Psi(c)}$.} $\Grothendieck{}{(-)} : \Sets^{C}\to\Cats$ on operators
we have a category of objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.
Equivalently, $\Grothendieck{}{\Operators}$ is the pullback of $\Operators$
along the universal $\Sets$-bundle where $\pi_{\Operators}$ is a discrete
Grothendieck fibration and $ap_{\Singleton}$ is the forgetful functor from pointed sets:

@@

Operators are defined by specifying the fibers of $\pi_{\Operators}$ in which
they reside. For instance, consider the lambda calculus with a single sort,
$\SortExp$; we give its signature by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\lambda}{
    \MkArity{\MkValence{\cdot}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathsf{ap}}{
    \MkArity{
      \MkValence{\cdot}{\cdot}{\SortExp},
      \MkValence{\cdot}{\cdot}{\SortExp}
    }{\SortExp}
  }
\end{gather*}
